Addressing climate change and development pressures in an urban estuary through habitat restoration planning

### 2022-07-28 manu-draft.qmd
back to qmd

---
title: "Addressing climate change and development pressures in an urban estuary through habitat restoration planning"
shorttitle: "Tampa Bay watershed habitat restoration planning"
output: 
  bookdown::word_document2:
    reference_docx: my_styles.docx
    number_sections: false
    pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
always_allow_html: true
bibliography: refs.bib
author: 
  - Gary E Raulerson:
      email: gmangrove@gmail.com
      institute: [TBEP]
      correspondence: false
  - Douglas E Robison:
      email: DRobison@esassoc.com 
      institute: [ESA]
      correspondence: false
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Maya C Burke:
      email: mburke@tbep.org
      institute: [TBEP]
      corrspondence: false
  - Justin Saarinen:
      email: justinsaarinen@gmail.com 
      institute: [ESA]
      correspondence: false
  - Christine Sciarrino:
      email: CSciarrino@esassoc.com 
      institute: [ESA]
      correspondence: false
  - Edward T Sherwood:
      email: esherwood@tbep.org 
      institute: [TBEP]
      correspondence: false
  - David A Tomasko:
      email: dave@sarasotabay.org
      institute: [SBEP]
      correspondence: false
institute:
  - TBEP: Tampa Bay Estuary Program, St. Petersburg, Florida 33701 USA
  - ESA: Environmental Science Associates, Tampa, Florida 33609 USA
  - SBEP: Sarasota Bay Estuary Program, Sarasota, Florida 34236 USA
link-citations: true
---

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
title: "Addressing climate change and development pressures in an urban estuary through habitat restoration planning"
shorttitle: "Tampa Bay watershed habitat restoration planning"
bibliography: refs.bib
author: 
  - name: Gary E Raulerson
    email: gmangrove@gmail.com
    affiliations: 
      - ref: tbep
    attributes:
      corresponding: false
  - name: Douglas E Robison
    email: DRobison@esassoc.com 
    affilations: 
      - ref: esa
    attributes:
      corresponding: false
  - name: Marcus W Beck
    email: mbeck@tbep.org
    affilations: 
      - ref: tbep
    attributes:
      corresponding: true
  - name: Maya C Burke
    email: mburke@tbep.org
    affilations: 
      - ref: tbep
    attributes:
      corresponding: false
  - name: Justin Saarinen
    email: justinsaarinen@gmail.com 
    affilations: 
      - ref: esa
    attributes:
      corresponding: false
  - name: Christine Sciarrino
    email: CSciarrino@esassoc.com 
    affilations: 
      - ref: esa
    attributes:
      corresponding: false
  - name: Edward T Sherwood
    email: esherwood@tbep.org 
    affilations: 
      - ref: tbep
    attributes:
      corresponding: false
  - name: David A Tomasko
    email: dave@sarasotabay.org
    affilations: 
      - ref: sbep
    attributes:
      corresponding: false
affiliations:
  - id: tbep
    name: Tampa Bay Estuary Program
    city: St. Petersburg
    state: Florida 
    postal-code: 33701 
    country: USA
  - id: esa
    name: Environmental Science Associates
    city: Tampa
    state: Florida
    postal-code: 33609 
    country: USA
  - id: sbep
    name: Sarasota Bay Estuary Program
    city: Sarasota
    state: Florida
    postal-code: 34236
    country: USA
---
